---
title: "Index.R"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F)
source("analysis.R")
```

## Summary
This report focuses on the shootings that occured during 2018, using crowd
sourced data. In 2018, there were `r num_shootings` shootings. The total amount 
of people injured in shootings during 2018 was `r people_injured` . The total 
amount of deaths that occured was `r lives_lost`. Some of the most dangerous 
states in the country include: Illinois, California, and Florida. These states 
rank in the top 3 in casualties and injuries. 

## (Top 10) Most Deaths by City
The table shown below shows the most impacted cities during 2018. The number 
represented is the number of deaths that have occured as a result. As shown 
below, with `r chicago_killed` casulaties, Chicago is the deadliest city in 2018. 
```{r}
kable(most_impacted_cities, col.names = c("City", "Number Killed"))
```

## (Top 10) Most Injuries by State
The table shown below shows the states with the most shooting injuries by during
2018. 
```{r}
kable(injured_by_state, col.names = c("State", "Number Injured"))
```

## Parkland Shooting
On `r parkland_date`, one of the [deadliest shootings](https://www.nytimes.com/2018/02/14/us/parkland-school-shooting.html) 
in recent history took place in `r parkland_city`, `r parkland_state`. This 
shooting took place at Stoneman Douglas High School (`r parkland_address`). This
tragic event resulted with a total of `r parkland_killed` people killed and an 
additional `r parkland_injured` people injured. Since then, the killer has been 
in custody and is awaiting a trial which will determine whether or not he will 
recieve the dealth penalty. The aftermath of this event has further increased 
the debate on the issue of gun control. Proponents of gun control cite this 
event as one of the reasons why more regulations need to be put in place. 


## Map of Shootings in the US
`r l`
This map displays all the shootings that involved deaths during 2018.


## Plot of Choice 
``` {r analysis, echo=FALSE}
  print(plot_final)
```

This plot groups the shootings dataset by month. The number of deaths and 
injuries is then evaluated and compared. As shown on the graph, the number of 
injuries per month is much greater than deaths per month. The number of injuries
peaks towards the middle of the year.




