---
title: "Index"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("propublica.R")
source("civic-info.R")
source("api-keys.R")
```

##Introduction
For this report, I am describing **Hawaii** and its _representatives_. The zip 
code utilized throughout this report is **96817**. This is the [link](https://www.googleapis.com/civicinfo/v2/representatives?key=AIzaSyBQaKwvFgJkkQQCApSgW6ksAFrlHh8quGg&address=96817) to the civic-info API. This is the [link](https://api.propublica.org/congress/v1/members/house/HI/current.json) to 
the propublica API. (There's something glitchy with the API key but I will try 
to insert this to the Read.ME file, its also imbedded in the propublica file)

##Hawaii's Representatives
```{r}
display_table
```


##Hawaii's House of Representatives Charts
```{r}
first_plot
```


```{r}
second_plot
```


##Tulsi Gabbard
Tulsi Gabbard is one of 2 representatives from the state of Hawaii. Her date of 
birth is `r dob_gabbard`, which would make her `r age_gabbard` years old. You 
can find Tulsi Gabbard on Twitter under the username **`r twitter_gabbard`**. 
In the past `r num_votes` votes in the 116th congress, Tulsi Gabbard voted "Yes" 
`r yes_votes` times. 







